\documentclass[11pt]{article}
\usepackage{graphicx}  % Include figure files
\usepackage{amsmath}  % Include figure files
\usepackage{xcolor}
\usepackage{tabularx}
\begin{document}
\title{SBSBBShower and SBSBBTotalShower}
\maketitle

\section{Introduction}
It is best to call the SBSBBTotalShower constructor in the replay script without a separate SBSBBShower contructor
for the PreShower and SHower. If one wants to
just setup either the PreShower or Shower , then one can call the BBShower contructor individually.
The SBSBBTotalShower constructor inherits from SBSCalorimeter. The  SBSBBTotalShower constructor
calls a Setup method which constructs both fShower and fPreShower from the SBSBBShower contructor.
SBSBBShower constructor inherits from the SBSCalorimeter and sets  SetModeADC(SBSModeADC::kWaveform) and
SetModeTDC(SBSModeTDC::kNone).



\section{ReadDatabase}
The SBSBBTotalShower::Init function calls the fShower::ReadDatabase and the fPreShower::ReadDatabase.
The SBSBBSHower::ReadDatabase first call the SBSCalorimeter::ReadDatabase. 
Then  additional parameters are optionally read in, but need to revisit these parameters.
The SBSBBTotalShower::ReadDatabase optional reads in additional parameters.
\begin{table}[h]
	\begin{center}
		\begin{tabularx}{\textwidth}{|c|X|c|}
			\hline 
			Parameter	& Description &  Global variable\\ 
			\hline
		thr\_adc	 &   & fThrADC \\
		\hline
		clus\_rad & & fClusRadius \\
		\hline
		mc\_data & & fMCdata \\
		\hline
		dxdydz & used only locally & dxyz \\
		\hline
\end{tabularx} 
\end{center}
\end{table}

\section{Decode}
SBSBBTotalShower::Decode calls fShower and fPreShower Decode methods.

\section{CoarseProcess}
SBSBBTotalShower::CoarseProcess first calls fShower and fPreShower CoarseProcess methods.
Then it calls  fShower and fPreShower MakeGoodBlocks methods.
It call fShower FindCluster method. {\color{red} Need to add method to match the preshower good blocks
with the shower clusters}

\section{FineProcess}
SBSBBTotalShower::FineProcess calls fShower FineProcess method.
{\color{red} Need to add fPreshower FineProcess call}








\end{document}
